%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,10pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{amssymb}
\usepackage{fontawesome5}
\usepackage{pifont}
\input{glyphtounicode}

\newcommand{\githubstars}[1]{[{\faGithubSquare}\,\ding{72}\,\textbf{#1}]}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-6pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-6pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-3pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-8pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-8pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-8pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-6pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Hyungtae Lim} \\ \vspace{1pt}
    \small
    \href{mailto:shapelim@mit.edu}{\underline{shapelim@mit.edu}} $|$
    \href{https://limhyungtae.github.io/hyungtae-lim/}{\underline{limhyungtae.github.io}} $|$
    \href{https://linkedin.com/in/hyungtae-lim}{\underline{linkedin.com/in/hyungtae-lim}} $|$
    \href{https://github.com/limhyungtae}{\underline{github.com/limhyungtae}}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Korea Advanced Institute of Science and Technology (KAIST)}{Daejeon, Korea}
      {Ph.D. in Electrical Engineering and Robotics Program}{Mar. 2020 -- Feb. 2023}
      \resumeItemListStart
        \resumeItem{Dissertation: ``Robust LiDAR SLAM for Autonomous Vehicles Leveraging Ground Segmentation''}
      \resumeItemListEnd
    \resumeSubheading
      {Korea Advanced Institute of Science and Technology (KAIST)}{Daejeon, Korea}
      {M.S. in Electrical Engineering and Robotics Program}{Mar. 2018 -- Feb. 2020}
    \resumeSubheading
      {Korea Advanced Institute of Science and Technology (KAIST)}{Daejeon, Korea}
      {B.S. in Mechanical Engineering}{Mar. 2013 -- Aug. 2018}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Postdoctoral Associate}{Apr. 2024 -- Present}
      {SPARK Lab, MIT (Advisor: Prof. Luca Carlone)}{Cambridge, MA}
      \resumeItemListStart
        \resumeItem{Lead research on large-scale multi-robot SLAM, enabling real-time, consistent 3D map building across multiple robots and sessions in complex urban environments.}
        \resumeItem{Mentor graduate and undergraduate researchers on 3D perception, autonomous mapping, and scene understanding systems.}
        \resumeItem{Maintainer of \href{https://github.com/MIT-SPARK/TEASER-plusplus}{TEASER++} \githubstars{2.1K}, \href{https://github.com/MIT-SPARK/Hydra}{Hydra} \githubstars{773}, \href{https://github.com/MIT-SPARK/KISS-Matcher}{KISS-Matcher} \githubstars{643}, \href{https://github.com/MIT-SPARK/VGGT-SLAM}{VGGT-SLAM} \githubstars{882}.}
      \resumeItemListEnd

    \resumeSubheading
      {Postdoctoral Fellow}{Mar. 2023 -- Mar. 2024}
      {Urban Robotics Lab, KAIST (Advisor: Prof. Hyun Myung)}{Daejeon, Korea}
      \resumeItemListStart
        \resumeItem{Developed real-time LiDAR-inertial and visual SLAM pipelines for robust autonomous navigation in dynamic real-world environments.}
        \resumeItem{Designed deep learning perception modules for dynamic obstacle detection, improving mapping reliability in crowded and unstructured scenes.}
      \resumeItemListEnd

    \resumeSubheading
      {Visiting Scholar}{Nov. 2022 -- Feb. 2023}
      {StachnissLab, University of Bonn (Advisor: Prof. Cyrill Stachniss)}{Bonn, Germany}
      \resumeItemListStart
        \resumeItem{Built ERASOR2: an instance-aware dynamic object removal system enabling high-fidelity static LiDAR map building in dynamic urban environments (RSS 2023).}
      \resumeItemListEnd

    \resumeSubheading
      {Research Intern}{Apr. 2022 -- Sep. 2022}
      {NAVER LABS}{Gyeonggi-Do, Korea}
      \resumeItemListStart
        \resumeItem{Engineered ORORA, a radar odometry system robust to outliers enabling reliable localization in GPS-denied and featureless environments (IEEE ICRA 2023).}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------KEY OPEN-SOURCE PROJECTS-----------
\section{Key Open-Source Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\href{https://github.com/MIT-SPARK/KISS-Matcher}{\textbf{KISS-Matcher}} \githubstars{643} $|$ \emph{Point Cloud Registration}}{IEEE ICRA 2025}
          \resumeItemListStart
            \resumeItem{Real-time, robust 3D point cloud registration pipeline; serves as the backbone for large-scale multi-session LiDAR SLAM systems.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\href{https://github.com/MIT-SPARK/VGGT-SLAM}{\textbf{VGGT-SLAM}} \githubstars{882} $|$ \emph{Dense RGB SLAM}}{NeurIPS 2025}
          \resumeItemListStart
            \resumeItem{Dense real-time 3D scene reconstruction system with globally consistent trajectory estimation; enables production-grade RGB mapping.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\href{https://github.com/url-kaist/patchwork-plusplus}{\textbf{Patchwork++}} \githubstars{842} $|$ \emph{Ground Segmentation}}{IEEE/RSJ IROS 2022}
          \resumeItemListStart
            \resumeItem{Real-time LiDAR ground segmentation system deployed in autonomous driving and mobile robotics production pipelines.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\href{https://github.com/LimHyungTae/ERASOR}{\textbf{ERASOR}} \githubstars{494} $|$ \emph{Static Map Building}}{IEEE RA-L 2021}
          \resumeItemListStart
            \resumeItem{Dynamic object removal system enabling high-fidelity static LiDAR map building for long-term autonomous operation.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd


%-----------PUBLICATIONS-----------
\section{Publications}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     10\texttt{+} first-author papers at top-tier robotics and AI venues: IEEE ICRA, RSS, IEEE RA-L, NeurIPS, IEEE/CVF ICCV, IJRR
    }}
 \end{itemize}


%-----------HONORS \& AWARDS-----------
\section{Honors \& Awards}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{2025} -- IEEE ICRA'25 Outstanding Reviewer Award (5 awardees out of 7,641 reviewers) \\
     \textbf{2024} -- RSS Pioneers 2024 (30 selected out of 202 candidates) \\
     \textbf{2024} -- 1st Prize, HILTI SLAM Challenge in IEEE ICRA'24 \\
     \textbf{2023} -- Best Paper Award, IEEE RA-L (5 of 1,100 papers) \\
     \textbf{2023} -- 1st Prize, HILTI SLAM Challenge in IEEE ICRA'23 (63 international teams) \\
     \textbf{2023} -- CES'23 Innovation Award (via technology transfer with HILLS Robotics) \\
     \textbf{2022} -- 2nd Cash Prize, HILTI SLAM Challenge in IEEE ICRA'22 \\
     \textbf{2020} -- Student Best Paper Award, ICCAS
    }}
 \end{itemize}


%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Programming}{: C++, Python, CUDA, CMake} \\
     \textbf{Frameworks \& Tools}{: ROS/ROS2, PyTorch, OpenCV, Git, Docker} \\
     \textbf{Research Areas}{: SLAM, 3D LiDAR, Point Cloud Registration, Ground Segmentation, Sensor Fusion, Deep Learning} \\
     \textbf{Languages}{: Korean (Native), English (Fluent)}
    }}
 \end{itemize}


%-------------------------------------------
\end{document}
