
\begin{pubSubsectionNum}
%    \item Jinwoo Jeon, Byeongho Yu, \hyungtaelim, and Hyun Myung, ``Seeing Without Seeing: Improving Deep Inertial Odometry by Leveraging Virtual Inertial Flow,'' in \textit{CVF Int. Conf. Comput. Vis. (ICCV)}, 2023 (Submitted)
    \item Junho Choi, Kihwan Ryoo, Jeewon Kim, Taeyun Kim, Eungchang Lee, Myeongwoo Jeong, Kevin Christiansen Marsim, \hyungtaelim, and Hyun Myung, ``SaWa-ML: Structure-Aware Pose Correction and Weight Adaptation-Based Robust Multi-Robot Localization,'' in \textit{Proc. IEEE/RSJ Int. Conf. Intell. Robot. Syst. (IROS)}, 2025. \accepted
    \item \underline{Dominic Maggio}, \underline{\hyungtaelim}, and Luca Carlone, ``VGGT-SLAM: Dense RGB SLAM Optimized on the SL(4) Manifold,'' in \textit{Proc. Neural Information Processing Systems (NeurIPS)}, 2025. \accepted
    \item \underline{Minkyun Seo}, \underline{\hyungtaelim}, Kanghee Lee, Luca Carlone, and Jaesik Park, ``BUFFER-X: Towards Zero-Shot Point Cloud Registration in Diverse Scenes,'' in \textit{Proc. IEEE/CVF Int. Conf. Comput. Vis. (ICCV)}, 2025, pp. 3851--3862.
    \item \hyungtaelim, Daebeom Kim, Gunhee Shin, Jingnan Shi, Ignacio Vizzo, Hyun Myung, Jaesik Park, and Luca Carlone, ``KISS-Matcher: Fast and Robust Point Cloud Registration Revisited,'' in \textit{Proc. IEEE Int. Conf. Robot. Automat. (ICRA)}, Atlanta, U.S., May 19--23, 2025, pp. 11104--11111.
    \item Kihwan Ryoo, \hyungtaelim, and Hyun Myung, ``MambaGlue: Fast and Robust Local Feature Matching With Mamba,'' in \textit{Proc. IEEE Int. Conf. Robot. Automat. (ICRA)}, Atlanta, U.S., May 19--23, 2025. \accepted
    \item \underline{\hyungtaelim}, \underline{Seoyeon Jang}, Benedikt Mersch, Jens Behley, Hyun Myung, and Cyrill Stachniss, ``HeLiMOS: A Dataset for Moving Object Segmentation in 3D Point Clouds From Heterogeneous LiDAR Sensors,'' in \textit{Proc. IEEE/RSJ Int. Conf. Intell. Robot. Syst. (IROS)}, Abu Dhabi, UAE, Oct. 14--18, 2024.
    \item Changki Sung, Wanhee Kim, Jungho An, Wooju Lee, \underline{\hyungtaelim}, and \underline{Hyun Myung}, ``Contextrast: Contextual Contrastive Learning for Semantic Segmentation,'' in \textit{Proc. IEEE/CVF Conf. Comput. Vis. Pattern Recognit. (CVPR)}, Seattle, U.S., Jun. 17--21, 2024, pp. 3732--3742.
    \item Minho Oh, Gunhee Shin, Seoyeon Jang, Seungjae Lee, Dongkyu Lee, Wonho Song, Byeongho Yu, \hyungtaelim, Jaeyoung Lee, and Hyun Myung, ``B-TMS: Bayesian Traversable Terrain Modeling and Segmentation Across 3D LiDAR Scans and Maps for Enhanced Off-Road Navigation,'' in \textit{Proc. IEEE Intell. Veh. (IV)}, Jeju Island, Korea, Republic of, Jun. 2--5, 2024.
    \item Wooju Lee, Dasol Hong, \underline{\hyungtaelim}, and \underline{Hyun Myung}, ``Object-Aware Domain Generalization for Object Detection,'' in \textit{Annual AAAI Conf. Artif. Intell. (AAAI)}, Vancouver, Canada, Feb. 20--27, 2024, pp. 2946--2955.
    \item Seoyeon Jang, Minho Oh, Byeongho Yu, I Made Aswin Nahrendra, Seungjae Lee, \hyungtaelim, and Hyun Myung, ``TOSS: Real-time Tracking and Moving Object Segmentation for Static Scene Mapping,'' in \textit{Proc. Int. Conf. Robot Intell. Tech. Applications (RiTA)}, Xian, China, Dec. 6--8, 2023. \textbf{Received Best Paper Award}.
    \item Dong-Uk Seo, \hyungtaelim, Eungchang Mason Lee, Hyunjun Lim, and Hyun Myung, ``Enhancing Robustness of Line Tracking Through Semi-Dense Epipolar Search in Line-based SLAM,'' in \textit{Proc. IEEE/RSJ Int. Conf. Intell. Robot. Syst. (IROS)}, Detroit, U.S., Oct. 1--5, 2023, pp. 3483--3490.
    \item \hyungtaelim, Lucas Nunes, Benedikt Mersch, Xieyuanli Chen, Jens Behley, Hyun Myung, and Cyrill Stachniss, ``ERASOR2: Instance-Aware Robust 3D Mapping of the Static World in Dynamic Scenes,'' in \textit{Robotics: Science and Systems~(RSS)}, Daegu, South Korea, Jul. 15--19, 2023.
    \item \hyungtaelim, Daebeom Kim, Beomsoo Kim, and Hyun Myung, ``AdaLIO: Robust Adaptive LiDAR-Inertial Odometry in Degenerate Indoor Environments,'' in \textit{Proc. Int. Conf. Ubiquit. Robot. (UR)}, Hawaii, U.S., Jun. 25--28, 2023, pp. 48--53.
    \item \hyungtaelim, Kawon Han, Gunhee Shin, Giseop Kim, Songcheol Hong, and Hyun Myung, ``ORORA: Outlier-Robust Radar Odometry,'' in \textit{Proc. IEEE Int. Conf. Robot. Automat. (ICRA)}, London, UK, May 29--Jun. 2, 2023, pp. 2046--2053.
    \item Alex Junho Lee, \hyungtaelim, Minho Oh, Wonho Song, and Hyun Myung, ``Volumetric Vegetation Monitoring From LiDAR Scans With Ground Estimation,'' in \textit{Proc. Int. Conf. Control, Automat. Syst. (ICCAS)}, Busan, Republic of Korea, Nov. 27--Dec. 1, 2022, pp. 1378--1379.
    \item \underline{Seungjae Lee}, \underline{\hyungtaelim}, and Hyun Myung, ``Patchwork++: Fast and Robust Ground Segmentation Solving Partial Under-Segmentation Using 3D point cloud,'' in \textit{Proc. IEEE/RSJ Int. Conf. Intell. Robot. Syst. (IROS)}, Kyoto, Japan, Oct. 22--27, 2022, pp. 13276--13283.
    \item Sumin Hu, Yeeun Kim, \hyungtaelim, Alex Junho Lee, and Hyun Myung, ``eCDT: Event Clustering for Simultaneous Feature Detection and Tracking,'' in \textit{Proc. IEEE/RSJ Int. Conf. Intell. Robot. Syst. (IROS)}, Kyoto, Japan, Oct. 22--27, 2022, pp. 3808--3815.
    \item \underline{Dong-Uk Seo}, \underline{\hyungtaelim}, Seungjae Lee, and Hyun Myung, ``PaGO-LOAM: Robust ground- optimized LiDAR odometry,'' in \textit{Proc. Int. Conf. Ubiquit. Robot. (UR)}, Jeju, Republic of Korea, Jul. 4--6, 2022, pp. 1--7.
    \item \hyungtaelim, Suyong Yeon, Soohyun Ryu, Yonghan Lee, Youngji Kim, Jaeseong Yun, Euigon Jung, Donghwan Lee, and Hyun Myung, ``A Single Correspondence Is Enough: Robust Global Registration to Avoid Degeneracy in Urban Environments,'' in \textit{Proc. IEEE Int. Conf. Robot. Automat. (ICRA)}, Philadelphia, USA, May 23--27, 2022, pp. 8010--8017.
    \item Sungwon Hwang, \hyungtaelim, and Hyun Myung, ``Equivariance-Bridged SO(2)-Invariant Representation Learning Using Graph Convolutional Network,'' in \textit{Proc. British Machine Vis. Conf. (BMVC)}, Virtual, Oct. 22--25, 2021.
    \item Hyungyu Lee, Myeongwoo Jeong, Chanyoung Kim, \hyungtaelim, Changgue Park, Sungwon Hwang, and Hyun Myung, ``Low-level Pose Control of Tilting Multirotor for Wall Perching Tasks Using Reinforcement Learning,'' in \textit{Proc. IEEE/RSJ Int. Conf. Intell. Robot. Syst. (IROS)}, Prague, Czech Republic (Virtual), Sep. 27--Oct. 1, 2021, pp. 9669--9676.
    \item Eungchang Mason Lee, Junho Choi, \hyungtaelim, and Hyun Myung, ``REAL: Rapid Exploration With Active Loop-Closing Toward Large-Scale 3D Mapping Using UAVs,'' in \textit{Proc. IEEE/RSJ Int. Conf. Intell. Robot. Syst. (IROS)}, Prague, Czech Republic (Virtual), Sep. 27--Oct. 1, 2021, pp. 4194--4198.
    \item \hyungtaelim, Hyeonjae Gil, and Hyun Myung, ``MSDPN: Monocular Depth Prediction With Partial Laser Observation Using Multi-stage Neural Networks,'' in \textit{Proc. IEEE/RSJ Int. Conf. Intell. Robot. Syst. (IROS)}, Las Vegas, USA (Virtual), Oct. 24--Dec. 24, 2020, pp. 10750--10757.
    \item \hyungtaelim, Sungwon Hwang, Sungjae Shin, and Hyun Myung, ``Normal Distributions Transform is Enough: Real-Time 3D Scan Matching for Pose Correction of Mobile Robot Under Large Odometry Uncertainties,'' in \textit{Proc. Int. Conf. Control, Automat. Syst. (ICCAS)}, Busan, Republic of Korea, Oct. 13--16, 2020, pp. 1155--1161, \textbf{Received Student Best Paper Award}.
    \item \hyungtaelim, Changgue Park, and Hyun Myung, ``RONet: Real-Time Range-Only Indoor Localization via Stacked Bidirectional LSTM with Residual Attention,'' in \textit{Proc. IEEE/RSJ Int. Conf. Intell. Robot. Syst. (IROS)}, Macau, China, Nov. 4--8, 2019, pp. 3241--3247.
    \item Jungmo Koo, Changgue Park, \hyungtaelim, and Hyung Myung, ``Light-Weight Deep Neural Networks for Multi-Target Classification,`` in \textit{Proc. Int. Conf. Control, Automat. Syst. (ICCAS)}, Jeju, Republic of Korea, Oct. 15--18, 2019.
    \item Jieum Hyun, Taekjun Oh, \hyungtaelim, and Hyung Myung, ``UWB-Based Indoor Localization Using Ray-Tracing Algorithm,'' in \textit{Proc. Int. Conf. Ubiquit. Robot. (UR)}, Hawaii, USA, Jun. 24-27, 2019, pp. 98--101.
    \item \hyungtaelim, Jungmo Koo, Jieum Hyun, and Hyung Myung, ``Effective Indoor Robot Localization by Stacked Bidirectional LSTM Using Beacon-Based Range Measurements,'' in \textit{Proc. Int. Conf. Robot Intell. Tech. Applications (RiTA)}, Putrajaya, Malaysia, Dec. 16-18, 2018, pp. 144--151.
    \item \hyungtaelim, Jungmo Koo, Jieum Hyun, and Hyun Myung, ``Recurrent Neural Networks for Range-Based Indoor Robot Localization,'' in \textit{Proc. IEEE/RSJ Int. Conf. Intell. Robot. Syst. (IROS)}, Madrid, Spain, Oct. 1--5, 2018.
\end{pubSubsectionNum}

%

