\begin{pubSubsectionNum}
    \item \underline{\hyungtaelim}, \underline{Minkyun Seo}, Luca Carlone, and Jaesik Park, ``Towards Zero-Shot Point Cloud Registration Across Diverse Scales, Scenes, and Sensor Setups,'' in \textit{IEEE Trans. Pattern Anal. Mach. Intell. (T-PAMI)}, 2026. \underreview
    % \item \underline{Changki Sung}, \underline{\hyungtaelim}, Wanhee Kim, and Hyun Myung, ``Contextrast++: Robust Multi-Scale Contextual Contrastive Learning for Semantic Segmentation,'' \textit{IEEE Trans. Pattern Anal. Mach. Intell. (T-PAMI)}, 2025. \underreview
    \item \underline{\hyungtaelim}, \underline{Daebeom Kim}, and Hyun Myung, ``Multi-Mapcher: Loop Closure Detection-Free Heterogeneous LiDAR Multi-Session SLAM Leveraging Outlier-Robust Registration for Autonomous Vehicles,'' \textit{IEEE Trans. Intell. Veh. (T-IV)}, vol.~11, no.~2, pp. 338--351, 2026
    \item I Nahrendra, Byeongho Yu, Minho Oh, Dongkyu Lee, Seunghyun Lee, Hyeonwoo Lee, \hyungtaelim, and Hyun Myung, ``Obstacle-Aware Quadrupedal Locomotion With Resilient Multi-Modal Reinforcement Learning,'' \textit{IEEE Trans. Robot. (T-RO)}, vol.~42, pp.~819--836, 2026.
    \item Kevin Christiansen Marsim, Minho Oh, Byeongho Yu, Seungjae Lee, I Made Aswin Nahrendra, \hyungtaelim, and Hyun Myung, ``LVI-Q: Robust LiDAR-Visual-Inertial-Kinematic Odometry for Quadruped Robots Using Tightly-Coupled and Efficient Alternating Optimization,'' \textit{IEEE Robot. Automat. Lett. (RA-L)}, vol.~10, no.~10, pp. 10050--10057, 2025. 
    \item Daehan Lee, \hyungtaelim, and Soohee Han, ``GenZ-ICP: Generalizable and Degeneracy-Robust LiDAR Odometry Using an Adaptive Weighting,'' \textit{IEEE Robot. Automat. Lett. (RA-L)}, vol. 10, no. 1, pp. 152--159, Nov. 14, 2024.
    \item Seungwon Song, \hyungtaelim, Alex Junho Lee, and Hyun Myung, ``DynaVINS++: Robust Visual-Inertial State Estimator in Dynamic Environments by Adaptive Truncated Least Squares and Stable State Recovery,'' \textit{IEEE Robot. Automat. Lett. (RA-L)}, vol. 9, no. 10, pp. 9127--9134, Sep. 6, 2024.
    \item {DongKi Noh, \hyungtaelim, Gyuho Eoh, Duckyu Choi, Jeong-Sik Choi, Hyunjun Lim, Seung-Min Baek, and Hyun Myung, ``CLOi-Mapper: Consistent, Lightweight, Robust, and Incremental Mapper With Embedded Systems for Commercial Robot Services,'' \textit{IEEE Robot. Automat. Lett. (RA-L)}, vol. 9, no. 9, pp. 7541--7548, Jul. 15, 2024}.
    \item {{\hyungtaelim}, Minho Oh, Seungjae Lee, Seunguk Ahn, and Hyun Myung, ``Similar but Different: A Survey of Ground Segmentation and Traversability Estimation for Terrestrial Robots,'' \textit{Int. J. Control, Automat. Syst. (IJCAS)}, vol. 22, pp. 347--359, Feb. 1, 2024}.
    \item {{\hyungtaelim}, Beomsoo Kim, Daebeom Kim, Eungchang Mason Lee, and Hyun Myung, ``Quatro++: Robust Global Registration Exploiting Ground Segmentation for Loop Closing in LiDAR SLAM,'' \textit{Int. J. Robot. Res. (IJRR)}, vol.~43, no.~5, pp. 685--715, Nov. 2, 2023}.
%    \item {\hyungtaelim, Seungjae Lee, Minho Oh, Changki Sung, Byeongho Yu, Dong-Uk Seo, and Hyun Myung, ``Patchwork2: Fast and Outlier-Robust Cascaded Ground Segmentation for Terrestrial Robots,'' \textit{IEEE Trans. Robot. (T-RO)}, 2023 (Under revision)}
    \item Alex Junho Lee, Seungwon Song, \hyungtaelim, Wooju Lee, and Hyun Myung, ``$(LC)^2$: LiDAR-Camera Loop Constraints For Cross-Modal Place Recognition,'' \textit{IEEE Robot. Automat. Lett. (RA-L)}, vol. 8, no. 6, pp. 3589--3596, Apr. 20, 2023.
    \item DongKi Noh, Changki Sung, Teayoung Uhm, Wooju Lee, \hyungtaelim, Jaeseok Choi, Kyuewang Lee, Dasol Hong, Daeho Um, Inseop Chung, Hochul Shin, MinJung Kim, Hyoung-Rock Kim, SeungMin Baek, and Hyun Myung, ``X-MAS: Extremely Large-Scale Multi-Modal Sensor Dataset for Outdoor Surveillance in Real Environments,'' \textit{IEEE Robot. Automat. Lett. (RA-L)}, vol. 8, no. 2, pp. 1093--1100, Jan. 12, 2023.
    \item Seungwon Song, \hyungtaelim, Alex Junho Lee, and Hyun Myung, ``DynaVINS: A Visual-Inertial SLAM for Dynamic Environments,'' \textit{IEEE Robot. Automat. Lett. (RA-L)}, vol. 7, no. 4, pp. 11523--11530, Oct. 31, 2022.
    \item \underline{Minho Oh}, \underline{Euigon Jung}, \hyungtaelim, Wonho Song, Sumin Hu, Eungchang Mason Lee, Junghee Park, Jaekyung Kim, Jangwoo Lee, and Hyun Myung, ``TRAVEL: Traversable Ground and Above-Ground Object Segmentation Using Graph Representation of 3D LiDAR Scans,'' \textit{IEEE Robot. Automat. Lett. (RA-L)}, vol. 7, no. 3, pp. 7255--7262, Jun. 13, 2022. \textbf{Won 2022 IEEE RA-L Best Paper Award}.
    \item Seungwon Song, \hyungtaelim, and Hyun Myung, ``G2P-SLAM: Generalized RGB-D SLAM Framework for Mobile Robots in Low-Dynamic Environments,'' \textit{IEEE Access}, vol. 10, pp. 21370--21383, Feb. 11, 2022.
    \item Changki Sung, Seulgi Jeon, \hyungtaelim, and Hyun Myung, ``What If There Was No Revisit? Large-Scale Graph-based SLAM with Traffic Sign Detection in an HD Map Using LiDAR Inertial Odometry,'' \textit{J. Intell. Serv. Robot.}, pp. 1--10, Nov. 25, 2021.
    \item \hyungtaelim, Hanseok Ryu, Matthew Rhudy, Dongjin Lee, Dongjin Jang, Changho Lee, Young-min Park, \underline{Wonkeun Youn}, and \underline{Hyun Myung}, ``Deep Learning-Aided Synthetic Airspeed Estimation of UAVs for Analytical Redundancy with a Temporal Convolutional Network,'' \textit{IEEE Robot. Automat. Lett. (RA-L)}, vol. 7, no. 1, pp. 17--24, Oct. 1, 2021.
    \item \hyungtaelim, Minho Oh, and Hyun Myung, ``Patchwork: Concentric Zone-Based Region-Wise Ground Segmentation With Ground Likelihood Estimation Using a 3D LiDAR Sensor,'' \textit{IEEE Robot. Automat. Lett. (RA-L) with IROS}, vol. 6, no. 4, pp. 6458--6465, Jun. 28, 2021.
    \item \underline{Wonkeun Youn}, \underline{\hyungtaelim}, Hyoung Sik Choi, Matthew B. Rhudy, Hyeok Ryu, Sungyug Kim, and Hyun Myung, ``State Estimation of HALE UAV With Deep Learning-Aided Virtual AOA/SSA Sensor for Analytical Redundancy,'' \textit{IEEE Robot. Automat. Lett. (RA-L)}, vol. 6, no. 3, pp. 5276--5283, Apr. 19, 2021.
    \item \hyungtaelim, Sungwon Hwang, and Hyun Myung, ``ERASOR: Egocentric Ratio of Pseudo Occupancy-Based Dynamic Object Removal for Static 3D Point Cloud Map Building,'' \textit{IEEE Robot. Automat. Lett. (RA-L) with ICRA}, vol. 6, no. 2, pp. 2272--2279, Feb. 23, 2021.
\end{pubSubsectionNum}

