%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience (Including Internship)}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {SPARK Lab, MIT} % Job title
    {Postdoctoral Associate} % Organization
    {Massachusetts, the U.S.} % Location
    {Apr. 2024 - Current} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item Advised by \href{https://lucacarlone.mit.edu/}{Prof. Luca Carlone}.
        \item Conduct research on multi-robot/-session autonomous mapping algorithms in complex urban environments.
        \item Guide and supervise graduate and undergraduate students in their research papers and thesis projects.
      \end{cvitems}
    }

 \cventry
    {Urban Robotics Lab, KAIST} % Job title
    {Postdoctoral Fellow} % Organization
    {Daejeon, Republic of Korea} % Location
    {Mar. 2023 - Mar. 2024} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item Advised by \href{https://urobot.kaist.ac.kr/url_teams/prof-hyunmyung/}{Prof. Hyun Myung}.
        \item Conducted research on localization and mapping techniques using LiDAR and vision data, respectively.
        \item Developed deep learning models for robust perception.
        \item Guided and supervised graduate and undergraduate students in their research papers and thesis projects.
      \end{cvitems}
    }

  \cventry
    {LG Electronics Co. Ltd.} % Job title
    {Outside Expert of the CTO Division of LG Electronics Co. Ltd.} % Organization
    {Republic of Korea} % Location
    {Mar. 2022 - Feb. 2023} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item Introduced state-of-the-art SLAM technologies and provided insights into future technological directions for mobile robots.
        \item Delivered a lecture entitled \textit{``Introduction to the latest SLAM technology trends and Semantic SLAM.''}
      \end{cvitems}
    }

  \cventry
    {StachnissLab} % Job title
    {Visiting Scholar} % Organization
    {Bonn, Germany} % Location
    {Nov. 2022 - Feb. 2023} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item After defending my dissertation, I visited Prof. Cyrill Stachniss' lab.
        \item Worked on an improved version of static map building.
        \item Submitted and had a paper accepted at RSS 2023 titled \textit{ERASOR2}.
      \end{cvitems}
    }

  \cventry
    {NAVER LABS} % Job title
    {Research Intern} % Organization
    {Gyeonggi-Do, Republic of Korea} % Location
    {Apr. 2022 - Sep. 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item Served as a Ph.D. research intern.
        \item Worked on robust global registration using 3D point cloud data captured by the LiDAR sensor.
        \item Submitted and accepted a paper to IEEE ICRA 2022.
        \item Relevant code: \href{https://github.com/url-kaist/Quatro}{\texttt{https://github.com/url-kaist/Quatro}}.
      \end{cvitems}
    }
%---------------------------------------------------------
\end{cventries}
